Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip

### 2014-05-26 PAPER/implementation.tex
some error fixed

Regarding the power consumption of whole \disr{} devices, 
we avoided an accurate power analysis with the switch activity
annotation due to the fact that \disr{} circuitry will be active 
only once during system startup. Indeed, after the setup phase, 
when all segments are mapped, the \disr{} block will stop its activity 
passing all the information related to segments to the routing
algorithm. For this reason the dynamic power falls to zero and
the only consumption could be due to the leakage
consumption. Finally with the reported results a coparison between 
RPF configuration circuits and the proposed circuits could be performed.
in particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}. In this work, as reported,  the implementation of the RPF requires an overhead of about 1692 CNFET for a $100 \times 100$ network. Furthemore, regarding the power consumption, this last implementation require a setup phase beyond which, the consumptions tends to zero. Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.

>>>>

Regarding the power consumption of whole \disr{} devices, 
we avoided an accurate power analysis with the switch activity
annotation due to the fact that \disr{} circuitry will be active 
only once during system startup. Indeed, after the setup phase, 
when all segments are mapped, the \disr{} block will stop its activity 
passing all the information related to segments to the routing
algorithm. For this reason the dynamic power falls to zero and
the only consumption could be due to the leakage
consumption. Finally, with the reported results, a coparison between 
RPF configuration circuits and the proposed circuits could be performed.
In particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}. As reported in this work,  the implemented hardware requires an overhead of about 1692 CNFET for a $100 \times 100$ network. Furthemore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero. Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.
